---
title: "HousingPricePrediction"
author: "Hyun Ko"
date: '2022-08-21'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_chunk$set(fig.width=10, fig.height=7.5) 
rm(list = ls())
library(tidyverse)
library(dplyr)
library(GGally)

# install.packages("ggpubr")
library(ggpubr)
```



```{r cars}
house <- read.csv('kc_house_data.csv')
head(house)
```

## 1. Exploratory Data Analysis

## EDA

- id: Unique ID for each home sold 
- date: Date of the home sale 
- price: Price of each home sold
- bedrooms: Number of bedroom 
bathrooms: Number of bathrooms, where .5 accounts for a room with a toilet but no shower
- sqft_living: Square footage of the apartments interior living space 
- sqft_lot: Square footage of the land space
- floors: Number of floors
- waterfront: A dummy variable for whether the apartment was overlooking the waterfront or not 
- view: An index from 0 to 4 of how good the view of the property was 
- condition: An index from 1 to 5 on the condition of the apartment,
- grade: An index from 1 to 13, where 1-3 falls short of building construction and design, 7 has an average level of                  
      construction and design, and 11-13 have a high quality level of construction and design.
- sqft_above: The square footage of the interior housing space that is above ground level 
- sqft_basement: The square footage of the interior housing space that is below ground level 
- yr_built: The year the house was initially built
- yr_renovated: The year of the house’s last renovation
- zipcode: What zipcode area the house is in 
- lat: Lattitude 
- long: Longitude 
- sqft_living15: The square footage of interior housing living space for the nearest 15 neighbors 
- sqft_lot15: The square footage of the land lots of the nearest 15 neighbors

```{r}
house <- house %>% dplyr::select(-id, -date, -lat, -long, -zipcode)
head(house)
```

```{r}
x <- unique(house$yr_renovated)
hist(house$yr_renovated)
```


```{r}
is.null(house)
```


```{r}
col_order <- c("price", "bedrooms", "bathrooms", "floors", "waterfront", "view", "condition", "grade", "yr_built",
               "yr_renovated", "sqft_living", "sqft_lot", "sqft_living15", "sqft_lot15")
house <- house[, col_order]
head(house)
```

```{r}
house$bathrooms <- round(house$bathrooms)

house_1 <- house %>% dplyr::select(price, bedrooms, bathrooms, floors)
ggpairs(house_1)
```

```{r}
p1 <- ggplot(house, aes(x = as.factor(bedrooms), y = price, fill = as.factor(bedrooms))) +
  geom_boxplot() +
  labs(x = "Number of Bedrooms", y = "Price", title = "Price by Number of Bedrooms", fill = "Bedrooms")

p2 <- ggplot(house, aes(x = as.factor(bathrooms), y = price, fill = as.factor(bathrooms))) +
  geom_boxplot() +
  labs(x = "Number of Bathrooms", y = "Price", title = "Price by Number of Bathrooms", fill = "Bathrooms")

p3 <- ggplot(house, aes(x = as.factor(floors), y = price, fill = as.factor(floors))) +
  geom_boxplot() +
  labs(x = "Number of Floors", y = "Price", title = "Price by Number of Floors", fill = "Floors")

ggarrange(p1, p2, p3,
                    labels = c("A", "B", "C"),
                    ncol = 1, nrow = 3)
```

```{r}
house_2 <- house %>% dplyr::select(waterfront, view, condition, price)
ggpairs(house_2)
```

```{r}
p4 <- ggplot(house, aes(x = as.factor(waterfront), y = price, fill = as.factor(waterfront))) +
  geom_boxplot() +
  labs(x = "Waterfront", y = "Price", title = "Price by with / without waterfront", fill = "Waterfront")

p5 <- ggplot(house, aes(x = as.factor(view), y = price, fill = as.factor(view))) +
  geom_boxplot() +
  labs(x = "View", y = "Price", title = "Price by View", fill = "View")

p6 <- ggplot(house, aes(x = as.factor(condition), y = price, fill = as.factor(condition))) +
  geom_boxplot() +
  labs(x = "Condition", y = "Price", title = "Price by Condition", fill = "Condition")

ggarrange(p4, p5, p6,
                    labels = c("A", "B", "C"),
                    ncol = 1, nrow = 3)
```

```{r}
house$yr_built <- case_when(
  (1900 <= house$yr_built) &  (house$yr_built< 1920) ~ 0,
  (1920 <= house$yr_built) &  (house$yr_built< 1940) ~ 1,
  (1940 <= house$yr_built) &  (house$yr_built< 1960) ~ 2,
  (1960 <= house$yr_built) &  (house$yr_built< 1980) ~ 3,
  (1980 <= house$yr_built) &  (house$yr_built< 2000) ~ 4,
  (2000 <= house$yr_built) ~ 5)

house$renovated <- ifelse(house$yr_renovated != 0, 1, 0)

house <- house %>% dplyr::select(-yr_renovated)
```

```{r}
house_3 <- house %>% dplyr::select(grade, yr_built, renovated, price)
ggpairs(house_3)
```



```{r}
p7 <- ggplot(house, aes(x = as.factor(grade), y = price, fill = as.factor(grade))) +
  geom_boxplot() +
  labs(x = "Grade", y = "Price", title = "Price by Grade", fill = "Grade")

p8 <- ggplot(house, aes(x = as.factor(yr_built), y = price, fill = as.factor(yr_built))) +
  geom_boxplot() +
  labs(x = "Year built", y = "Price", title = "Price by Year built", fill = "Year built")

p9 <- ggplot(house, aes(x = as.factor(renovated), y = price, fill = as.factor(renovated))) +
  geom_boxplot() +
  labs(x = "Renovated", y = "Price", title = "Price by Renovated", fill = "Renovated")

ggarrange(p7, p8, p9,
                    labels = c("A", "B", "C"),
                    ncol = 1, nrow = 3)
```


```{r}
house_4 <- house %>% dplyr::select(sqft_living, sqft_lot, price)
ggpairs(house_4)
```

```{r}
p10 <- ggplot(house, aes(x = sqft_living, y = price)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Sqft Living", y = "Price", title = "A Scatterplot of Sqft Living vs Price") 

p11 <- ggplot(house, aes(x = sqft_lot, y = price)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Sqft Lot", y = "Price", title = "A Scatterplot of Sqft Lot vs Price")


ggarrange(p10, p11,
                    labels = c("A", "B"),
                    ncol = 1, nrow = 2)
```
```{r}
house_5 <- house %>% dplyr::select(sqft_living15, sqft_lot15, price)
ggpairs(house_5)
```

```{r}
p12 <- ggplot(house, aes(x = sqft_living15, y = price)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Sqft Living15", y = "Price", title = "A Scatterplot of Sqft Living 15 vs Price") 

p13 <- ggplot(house, aes(x = sqft_lot15, y = price)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Sqft Lot15", y = "Price", title = "A Scatterplot of Sqft Lot 15 vs Price")


ggarrange(p12, p13,
                    labels = c("A", "B"),
                    ncol = 1, nrow = 2)
```

```{r}
mydata.cor <- cor(house)

palette = colorRampPalette(c("green", "white", "red")) (20)
heatmap(x = mydata.cor, col = palette, symm = TRUE, main = "A Heatmap of All Columns")
```



## 2. Train / Test Split
```{r}
set.seed(1) ##for reproducibility to get the same split
sample<-sample.int(nrow(house), floor(.80*nrow(house)), replace = F)
train<-house[sample, ] ##training data frame
test<-house[-sample, ] ##test data frame
head(train)
```



## 3. Modeling

< Stepwise Regression > 

```{r}
regnull <- lm(price ~ 1, data = train)
regfull <- lm(price ~ ., data = train)
step(regnull, scope = list(lower = regnull, upper = regfull), direction = "both")
```

< Forward Selection > 

```{r}
step(regnull, scope=list(lower=regnull, upper=regfull), direction="forward")
```


< Backward Elimination > 

```{r}
step(regfull, scope=list(lower=regnull, upper=regfull), direction="backward")
```

< Linear Regression >

: Every predictor but sqft_lot was chosen.

=> Every predictor is statistically significant, but what's counterintuitive that the sign of coefficient of bedrooms and sqft_lot15 is negative. This implies the prseence of multicollinearity among few columns. 

```{r}
result <- lm(price ~ bedrooms + bathrooms + floors + waterfront + view + condition + grade + yr_built + sqft_living + 
               sqft_living15 + sqft_lot15 + renovated, data = train)
summary(result)

test$predict <- round(predict(result, newdata = test) ^ 10)

test_mse_ln <- mean((test$price - test$predict)^2)
test_mse_ln

summary(result)$r.squared
summary(result)$adj.r.squared

PRESS <- function(linear.model) { 
  ## get the residuals from the linear.model. ## extract hat from lm.influence to obtain the leverages 
  pr <- residuals(linear.model) / (1-lm.influence(linear.model)$hat)
  ## calculate the PRESS by squaring each term and adding them up 
  PRESS <- sum(pr ^ 2) 
  return(PRESS) 
}

PRESS(result)

##Find SST 
anova_result<-anova(result) 
SST<-sum(anova_result$"Sum Sq") ##R2 pred 
Rsq_pred <- 1-PRESS(result)/SST 
Rsq_pred
```

However, according to VIFs, all numbers are below threshold.

```{r}
library(faraway)
vif(result)
```

Let's check residual plot. It seems that linear assumption is violated: constant varaince. Variance gets larger as fitted y gets larger.
Therefore, we should implement y transformation to address this issue.

```{r}
yhat <- result$fitted.values
res <- result$residuals
Data <- data.frame(train, yhat, res)

ggplot(Data, aes(x=yhat,y=res))+
  geom_point()+
  geom_hline(yintercept=0, color="red")+
  labs(x="Fitted y",
       y="Residuals",
       title="Residual Plot")

acf(res)
qqnorm(res)
qqline(res, col="red")
```


```{r}
library(MASS)
boxcox(result,lambda = seq(-1.,1,0.5))
```


```{r}
train <- train %>% mutate(price = price ^ 0.1)
result2 <- lm(price ~ bedrooms + bathrooms + floors + waterfront + view + condition + grade + yr_built + sqft_living + 
               sqft_living15 + sqft_lot15 + renovated, data = train)
summary(result2)

summary(result2)$r.squared
summary(result2)$adj.r.squared


PRESS(result2)

##Find SST 
anova_result<-anova(result2) 
SST<-sum(anova_result$"Sum Sq") 

##R2 pred 
Rsq_pred <- 1-PRESS(result2)/SST 
Rsq_pred
```

```{r}
yhat<-result2$fitted.values 
res<-result2$residuals
Data<-data.frame(train,yhat,res)

ggplot(Data, aes(x=yhat,y=res))+
  geom_point()+
  geom_hline(yintercept=0, color="red")+
  labs(x="Fitted y",
       y="Residuals",
       title="Residual Plot")

acf(res)
qqnorm(res)
qqline(res, col="red")

test$predict <- round(predict(result2, newdata = test) ^ 10)
test_mse_ln_2 <- mean((test$price - test$predict)^2)
test_mse_ln_2

tail(test)
```

```{r}
a <- data.frame(price = c(10000, 20000, 30000))
a <- a %>% mutate(boxcox = price^0.1, retransform = boxcox ^ 10)
a
```


## 4. Identifying Outliers, High Leverage Points, and Influential Points

```{r}
head(train)
```


```{r}
boxplot(train$price)
```


< Outlier Detection > 
: NO Outlier in train data.

```{r}
n <- nrow(train)
p <- 13
cv <- qt(1-0.05,(2*n), n-1-p)
res <- result2$residuals
standard.res<- res/summary(result2)$sigma
student.res <- rstandard(result2)
ext.student.res <- rstudent(result2)

ext.student.res[abs(ext.student.res)>cv]

res.frame<-data.frame(res,standard.res,
                      student.res,ext.student.res)
```


```{r}
par(mfrow=c(1,3))
plot(result2$fitted.values,standard.res,
     main="Standardized Residuals",
     ylim=c(-4.5,4.5))
plot(result2$fitted.values,student.res,
     main="Studentized Residuals",
     ylim=c(-4.5,4.5))
plot(result2$fitted.values,ext.student.res,
     main="Externally  Studentized Residuals",
     ylim=c(-4.5,4.5))
```



< Leverage > 

: Total 1604 observations (about 9.3 %) are far from the centroid of the predictor space. These high leverage points are potentially to be influential observations.

```{r}
# leverage
lev <- lm.influence(result2)$hat

# identify high leverage points
x <- lev[lev > 2 * p / n]
length(x) / n
```


< Detecting Influential Observations >

- An observation is problematic only insofar as it "disagrees" with the observation of the data.
- After finding the observations that are outlying / high leverage, the next step is to ascertain whether or not these observations are influential.
- Measures of influence address how much estimates (fitted values, coefficients, etc..) will change if observation was deleted.

```{r}
# COOK's Distance
COOKS<-cooks.distance(result2)
y <- COOKS[COOKS>qf(0.5,p,n-p)]
length(y)
```


```{r}
# DFFITS (Difference in Fits)
DFFITS <- dffits(result2)
z <- (DFFITS[abs(DFFITS)>2*sqrt(p/n)])
z
```

```{r}
data.frame(z)

indices <- rownames(data.frame(z))
```

```{r}
head(train)

rownames(head(train))
l <- head(train) %>% filter(rownames(head(train)) != 17401)
l <- l %>% filter()
#train[rownames(train) == 17401]
```


```{r}
train2 <- train
train2$indices <- rownames(train2)
#train2
for (i in indices) {
  train2 <- train2 %>% filter(indices != i)
}

nrow(train2)
```


```{r}
length(unique(indices))

nrow(train) - nrow(train2)
length(indices)
```



```{r}
result3 <- lm(price ~ bedrooms + bathrooms + floors + waterfront + view + condition + grade + yr_built + sqft_living + 
               sqft_living15 + sqft_lot15 + renovated, data = train2)
summary(result3)

test$predict <- round(predict(result2, newdata = test) ^ 10)
test_mse_ln_3 <- mean((test$price - test$predict)^2)
test_mse_ln_3

summary(result3)$r.squared
summary(result3)$adj.r.squared


PRESS(result3)

##Find SST 
anova_result<-anova(result3) 
SST <- sum(anova_result$"Sum Sq") 

##R2 pred 
Rsq_pred <- 1-PRESS(result3)/SST 
Rsq_pred

yhat<-result3$fitted.values 
res<-result3$residuals
Data<-data.frame(train2,yhat,res)

ggplot(Data, aes(x=yhat,y=res))+
  geom_point()+
  geom_hline(yintercept=0, color="red")+
  labs(x="Fitted y",
       y="Residuals",
       title="Residual Plot")

acf(res)
qqnorm(res)
qqline(res, col="red")
```

```{r}
head(test)
```


```{r}

```











