---
title: "HousingPricePrediction"
author: "Hyun Ko"
date: '2022-08-21'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=10, fig.height=7.5) 
rm(list = ls())
library(tidyverse)
library(dplyr)
library(GGally)

# install.packages("ggpubr")
library(ggpubr)
```



```{r cars}
house <- read.csv('kc_house_data.csv')
head(house)
```

## 1. Exploratory Data Analysis

## EDA

- id: Unique ID for each home sold 
- date: Date of the home sale 
- price: Price of each home sold
- bedrooms: Number of bedroom 
bathrooms: Number of bathrooms, where .5 accounts for a room with a toilet but no shower
- sqft_living: Square footage of the apartments interior living space 
- sqft_lot: Square footage of the land space
- floors: Number of floors
- waterfront: A dummy variable for whether the apartment was overlooking the waterfront or not 
- view: An index from 0 to 4 of how good the view of the property was 
- condition: An index from 1 to 5 on the condition of the apartment,
- grade: An index from 1 to 13, where 1-3 falls short of building construction and design, 7 has an average level of                  
      construction and design, and 11-13 have a high quality level of construction and design.
- sqft_above: The square footage of the interior housing space that is above ground level 
- sqft_basement: The square footage of the interior housing space that is below ground level 
- yr_built: The year the house was initially built
- yr_renovated: The year of the house’s last renovation
- zipcode: What zipcode area the house is in 
- lat: Lattitude 
- long: Longitude 
- sqft_living15: The square footage of interior housing living space for the nearest 15 neighbors 
- sqft_lot15: The square footage of the land lots of the nearest 15 neighbors

```{r}
house <- house %>% select(-id, -date, -lat, -long, -zipcode)
head(house)
```

```{r}
x <- unique(house$yr_renovated)
hist(house$yr_renovated)
```


```{r}
is.null(house)
```


```{r}
col_order <- c("price", "bedrooms", "bathrooms", "floors", "waterfront", "view", "condition", "grade", "yr_built",
               "yr_renovated", "sqft_living", "sqft_lot", "sqft_living15", "sqft_lot15")
house <- house[, col_order]
head(house)
```

```{r}
house$bathrooms <- round(house$bathrooms)

house_1 <- house %>% select(price, bedrooms, bathrooms, floors)
ggpairs(house_1)
```

```{r}
p1 <- ggplot(house, aes(x = as.factor(bedrooms), y = price, fill = as.factor(bedrooms))) +
  geom_boxplot() +
  labs(x = "Number of Bedrooms", y = "Price", title = "Price by Number of Bedrooms", fill = "Bedrooms")

p2 <- ggplot(house, aes(x = as.factor(bathrooms), y = price, fill = as.factor(bathrooms))) +
  geom_boxplot() +
  labs(x = "Number of Bathrooms", y = "Price", title = "Price by Number of Bathrooms", fill = "Bathrooms")

p3 <- ggplot(house, aes(x = as.factor(floors), y = price, fill = as.factor(floors))) +
  geom_boxplot() +
  labs(x = "Number of Floors", y = "Price", title = "Price by Number of Floors", fill = "Floors")

ggarrange(p1, p2, p3,
                    labels = c("A", "B", "C"),
                    ncol = 1, nrow = 3)
```

```{r}
house_2 <- house %>% select(waterfront, view, condition, price)
ggpairs(house_2)
```

```{r}
p4 <- ggplot(house, aes(x = as.factor(waterfront), y = price, fill = as.factor(waterfront))) +
  geom_boxplot() +
  labs(x = "Waterfront", y = "Price", title = "Price by with / without waterfront", fill = "Waterfront")

p5 <- ggplot(house, aes(x = as.factor(view), y = price, fill = as.factor(view))) +
  geom_boxplot() +
  labs(x = "View", y = "Price", title = "Price by View", fill = "View")

p6 <- ggplot(house, aes(x = as.factor(condition), y = price, fill = as.factor(condition))) +
  geom_boxplot() +
  labs(x = "Condition", y = "Price", title = "Price by Condition", fill = "Condition")

ggarrange(p4, p5, p6,
                    labels = c("A", "B", "C"),
                    ncol = 1, nrow = 3)
```

```{r}
house$yr_built <- case_when(
  (1900 <= house$yr_built) &  (house$yr_built< 1920) ~ 0,
  (1920 <= house$yr_built) &  (house$yr_built< 1940) ~ 1,
  (1940 <= house$yr_built) &  (house$yr_built< 1960) ~ 2,
  (1960 <= house$yr_built) &  (house$yr_built< 1980) ~ 3,
  (1980 <= house$yr_built) &  (house$yr_built< 2000) ~ 4,
  (2000 <= house$yr_built) ~ 5)

house$renovated <- ifelse(house$yr_renovated != 0, 1, 0)

house <- house %>% select(-yr_renovated)
```

```{r}
house_3 <- house %>% select(grade, yr_built, renovated, price)
ggpairs(house_3)
```



```{r}
p7 <- ggplot(house, aes(x = as.factor(grade), y = price, fill = as.factor(grade))) +
  geom_boxplot() +
  labs(x = "Grade", y = "Price", title = "Price by Grade", fill = "Grade")

p8 <- ggplot(house, aes(x = as.factor(yr_built), y = price, fill = as.factor(yr_built))) +
  geom_boxplot() +
  labs(x = "Year built", y = "Price", title = "Price by Year built", fill = "Year built")

p9 <- ggplot(house, aes(x = as.factor(renovated), y = price, fill = as.factor(renovated))) +
  geom_boxplot() +
  labs(x = "Renovated", y = "Price", title = "Price by Renovated", fill = "Renovated")

ggarrange(p7, p8, p9,
                    labels = c("A", "B", "C"),
                    ncol = 1, nrow = 3)
```


```{r}
house_4 <- house %>% select(sqft_living, sqft_lot, price)
ggpairs(house_4)
```

```{r}
p10 <- ggplot(house, aes(x = sqft_living, y = price)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Sqft Living", y = "Price", title = "A Scatterplot of Sqft Living vs Price") 

p11 <- ggplot(house, aes(x = sqft_lot, y = price)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Sqft Lot", y = "Price", title = "A Scatterplot of Sqft Lot vs Price")


ggarrange(p10, p11,
                    labels = c("A", "B"),
                    ncol = 1, nrow = 2)
```
```{r}
house_5 <- house %>% select(sqft_living15, sqft_lot15, price)
ggpairs(house_5)
```

```{r}
p12 <- ggplot(house, aes(x = sqft_living15, y = price)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Sqft Living15", y = "Price", title = "A Scatterplot of Sqft Living 15 vs Price") 

p13 <- ggplot(house, aes(x = sqft_lot15, y = price)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Sqft Lot15", y = "Price", title = "A Scatterplot of Sqft Lot 15 vs Price")


ggarrange(p12, p13,
                    labels = c("A", "B"),
                    ncol = 1, nrow = 2)
```

```{r}
mydata.cor <- cor(house)

palette = colorRampPalette(c("green", "white", "red")) (20)
heatmap(x = mydata.cor, col = palette, symm = TRUE, main = "A Heatmap of All Columns")
```






```{r}
set.seed(1) ##for reproducibility to get the same split
sample<-sample.int(nrow(house), floor(.80*nrow(house)), replace = F)
train<-house[sample, ] ##training data frame
test<-house[-sample, ] ##test data frame
head(train)
```

